---
title: "EDA_viz"
author: "Rich Leung"
date: "December 24, 2014"
output: html_document
---


```{r declaration, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggvis)
library(dplyr)

# Initializing working directory
dir_Main       = "/Users/richleung/Dropbox/Projects/R/EDA"
dir_ADS_Summary 	= "/Users/richleung/Dropbox/Documents/Accenture/Walmart/g. ADS_Summary"
dir_ADS_BB			= "/Users/richleung/Dropbox/Documents/Accenture/Walmart/a. by Building Blocks"
setwd(dir_Main)



# Import input data set
setwd(dir_ADS_BB)
ADS_BB <- read.table("ADS_WMT__n_bldblk_updated07.csv", sep=",", header=TRUE)

setwd(dir_ADS_Summary)
Summ_BB <- read.table("Summary_BB.csv", sep=",", header=TRUE)

setwd(dir_Main)
```

The following are results of an Exploratory Data Analysis (EDA) using R.

1.) Cross-sectional plot of relationship between Price Perception and Market Share for all geographies (building blocks [41])
```{r x-sect_plot, message=FALSE, warning=FALSE}
tmp1 <- Summ_BB %>%
  select(Bldblk, C2_110_wgt_avg_21mo, sales_index_yrmon_strtyp_21MO, Trips_index_yrmon_strtyp_21MO, MKT_SHARE_Nielsen_21MO)

g1 <- tmp1 %>% 
	ggvis(~C2_110_wgt_avg_21mo, ~MKT_SHARE_Nielsen_21MO, fill := "darkblue") %>% 
	layer_points() %>% 
	layer_model_predictions(model = "lm", se = TRUE) %>%
	add_axis("x", title = "Price Perception (C2_110)") %>% 
	add_axis("y", title = "Market Share") %>% 
 	add_axis("x", orient = "top", ticks = 0, title = "Relationship btw Price Perception and Market Share by Building Block")
print(g1)
```





2.) Panel plot of relationship between Price Perception and Market Share for all geographies (building blocks [41]) and for all Year-Months (21-mo.)
```{r panel_plot, message=FALSE, warning=FALSE}
tmp1 <- ADS_BB %>%
  select(bldblk, C2_110_wgt, Sales_index_yrmon_strtyp, Trips_index_yrmon_strtyp, mkt_share_nielsen)

g1 <- tmp1 %>% 
	ggvis(~C2_110_wgt, ~mkt_share_nielsen, fill := "darkblue") %>% 
	layer_points() %>% 
	layer_model_predictions(model = "lm", se = TRUE) %>% 
	add_axis("x", title = "Price Perception (C2_110)") %>% 
	add_axis("y", title = "Market Share") %>% 
# 	add_title(title = "Relationship btw Price Perception & Market Share Index by Building Block")
	add_axis("x", orient = "top", ticks = 0, title = "Relationship btw Price Perception and Market Share by Building Block by Year-Months")
print(g1)
```





3.) Time-Series data

3a. Price Perception over time (21 mo.)
```{r timeseries_Price, message=FALSE, warning=FALSE}
tmp <- ADS_BB %>% 
  group_by(Wave) %>% 
	summarise_each(funs(mean(., na.rm = TRUE)), C2_110_wgt, Sales_index_yrmon_strtyp)

g <- tmp %>% 
	ggvis(~Wave, ~C2_110_wgt, stroke = ~Sales_index_yrmon_strtyp) %>% 
	layer_lines() %>% 
	add_axis("x", title = "Year-Months (wave)") %>% 
	add_axis("y", title = "Price Perception (C2_110)") %>% 
	add_axis("x", orient = "top", ticks = 0, title = "Price perception over time (21 mo.)") 
print (g)
```

3b. Market Share over time (21 mo.)
```{r timeseries_MS, message=FALSE, warning=FALSE}
tmp <- ADS_BB %>% 
  group_by(Wave) %>% 
	summarise_each(funs(mean(., na.rm = TRUE)), mkt_share_nielsen, Sales_index_yrmon_strtyp)

g <- tmp %>% 
	ggvis(~Wave, ~mkt_share_nielsen, stroke = ~Sales_index_yrmon_strtyp, stroke = ~Sales_index_yrmon_strtyp) %>% 
	layer_lines() %>% 
	add_axis("x", title = "Year-Months (wave)") %>% 
	add_axis("y", title = "Market Share") %>% 
	add_axis("x", orient = "top", ticks = 0, title = "Market Share over time (21 mo.)") 
print (g)
```